\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-22 manuscript/main.tex
update the latest result

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check By HHI Index}
    \label{tab:sylized_fact_hetero_hhi}
    \input{../result_tables/robust_hhi.tex}

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check By Market Maturity Index}
    \label{tab:sylized_fact_hetero_mature}
    \input{../result_tables/robust_mature.tex}

@@

>>>>

In the online Appendix \ref{tab:platform_consolidation_hetero_mature}, we present the heterogeneous effects of Lianjia's operations in both mature and immature markets. Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups. Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences. The treatment effect becomes significant only after the first period, aligning with our empirical findings.

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check By HHI Index}
    \label{tab:dynamic_hhi}
    \input{../result_tables/robust_hhi.tex}

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check By Market Maturity Index}
    \label{tab:platform_consolidation_hetero_mature}
    \input{../result_tables/robust_mature.tex}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/average_income_by_treatment_platform.pdf}
    \caption{Treatment Effect of platform consolidation}
    \label{fig:treatment_consolidation}
    Note: the x-axis is year and the y-axis is the average income of Lianjia in each year. The graph uses the neighborhood-level data.
\end{figure}
